Individual Variation in Animal Movement

### 2021-02-15 movement_paper/rudolph_ch2.Rmd
add state-space model citation

Providing a general framework for movement ecology that allows to link movement patterns and processes, starting with a focus on movement itself and the individual's internal state,navigation capacity, motion capacity, and responses to external factors [@nathan2008movement]. Although it increases the complexity and requires more fine scale data, the framework recognizes how variation at the level of individuals can have consequences at larger ecological scales.

>>>>

Providing a general framework for movement ecology that allows to link movement patterns and processes, starting with a focus on movement itself and the individual's internal state,navigation capacity, motion capacity, and responses to external factors [@nathan2008movement]. Although it increases the complexity and requires more fine scale data, the framework recognizes how variation at the level of individuals can have consequences at larger ecological scales. In this regard, state-space models (SSMs) have been suggested as flexible options to describe the general framework that incorporates observation error and noisy data, as it is common in the case of radiotelemetry data, and even the use of hierarchical structures or mixed-effects SSMs that can explicitly model variability across individuals [@patterson2008state].
